\LARGE \bf Cascading Situation Assessment for Robots

### 2017-02-27 paper.tex
Proof read part 4

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{l2tor-photo2}
    \caption{A user manipulating objects on RFID mat while an operator monitors
    the interaction via an {\tt uwds view} client}

@@

\uwds has been used within the European L2TOR project~\cite{belpaeme2015l2tor}
in order to conceptualize and visualize the spatial relations and visibility of
the physical objects that users interact with. In one of the scenarios of this
project, users are instructed by a NAO robot to manipulate a number of
Duplo-like animals on top of a printed background paper which serves as a
landscape (See \ref{fig|l2torexample}). The robot instructions are based on
pedagogical strategies to promote spatial relation learning by object
manipulation. Such instructions include commands like to place the elephant
\textit{on top} or \textit{next to} the cube or put the giraffe \textit{inside}
the house.  For that reason, the robot and the operator should be able to access
whether the user performs the required task and at the same time envisage their
perspective. A number of \uwds clients have been developed in order to provide a
distributed model of the environment and the robot as described in the next
section.

\subsection*{Architecture}
\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{l2tor}
    \caption{Schema of the \uwds architecture used in L2TOR project pilot study. }
    \label{fig|l2torarchitecture}
\end{figure}

The scenario consists of a number of \uwds clients distributed across two
computers that communicate with each other in order to provide an updated
representation of the world. Figure \ref{fig|l2torarchitecture} illustrates the
high level communication of the \uwds clients that form the architecture of the
L2TOR spatial relations platform.

L2TOR \uwds clients:

\begin{itemize}
    \item \textbf{Kinect Head Tracker} Captures the location and the direction
        of the user's head - Camera point

    \item \textbf{Object RFID tracker} Updates the locations of the virtual
        objects based on RFID data

    \item \textbf{NAO model} Virtual representation of the Robot - Camera poit

    \item \textbf{Visibility computation} Computes visibility based on camera
        points

    \item \textbf{Spatial Relations computation} Extracts spatial relations
        between the virtual objects

    \item \textbf{Game/Rules computation} Interaction manager based on \uwds
        clients' input

@@

The L2TOR project features an additional scenario where the user performs the
manipulations on a tablet computer instead of using physical objects. To
accommodate this change, we replaced the object detection \uwds client with a 3D
virtual object detection while the rest of the system remains the same. Finally,
we are evaluating the use of a hybrid platform that utilizes both virtual and
physical objects at the same time.

>>>>

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{l2tor-photo2}
    \caption{A user manipulating objects on top of a RFID mat (providing object
    localization) with a NAO robot, while an operator monitors
    the interaction on a tablet that display an {\tt uwds view} client.}

@@

\uwds has been used within the European L2TOR project~\cite{belpaeme2015l2tor}
in order to conceptualize and visualize the spatial relations and visibility of
the physical objects that participants interact with. In one of the scenarios of this
project, participants are instructed by a NAO robot to manipulate a number of
Duplo-like animals on top of a printed background paper which serves as a
landscape (Figure~\ref{fig|l2torexample}). The robot instructions are based on
pedagogical strategies to promote spatial relation learning by object
manipulation. Such instructions include commands like to place the elephant
\textit{on top} or \textit{next to} the cube or put the giraffe \textit{inside}
the house.  To assess the performance, the robot and the operator need to
compute spatial relation between objects from the visual perspective of the
participant.

\subsection*{Architecture}

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{l2tor}
    \caption{Schema of the \uwds architecture used in the L2TOR project. }
    \label{fig|l2torarchitecture}
\end{figure}

The interaction scenario requires a number of \uwds clients. The client are
distributed across two computers (the robot and a Microsoft Windows-operated
tablet) that communicate with each other in order to synchronize the worlds
representations. Figure~\ref{fig|l2torarchitecture} illustrates the topology of
the \uwds network, that consists in the following clients:

\begin{itemize}
    \item \textbf{Kinect Head Tracker}: captures the location and the direction
        of the user's head -- maintains the {\tt human} \emph{Perspective} node;

    \item \textbf{Object RFID tracker}: updates the locations of the virtual
        objects based on RFID data;

    \item \textbf{NAO joint state publisher}: virtual representation of the
        robot -- maintains the {\tt robot} \emph{Perspective} node;

    \item \textbf{Visibility computation}: computes visibility based on
        \emph{Perspective} nodes;

    \item \textbf{Spatial relations computation}: extracts symbolic spatial relations
        between the virtual objects;

    \item \textbf{Game/Rules computation}: interaction manager based on \uwds
        clients' input.

@@

The L2TOR project features an additional scenario where the user performs the
manipulations on a tablet computer instead of using physical objects. To
accommodate this change, we replaced the object detection \uwds client with a 3D
virtual object detection while the rest of the system remains the same.

Finally, we are evaluating the use of a hybrid platform that utilizes both virtual and
physical objects at the same time.
